Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 document/slides/slides.tex
Updates from Overleaf

\author[et al] % (optional)
{Barriga-Cabanillas,  Chiarella, Correa, Michuda}

@@

\date[Feb 2021] % (optional)
{CIGAT \\
February 2021}

@@

\textbf{We study how these heterogeneity mask the true impact of adoption}

@@

Correlated Random Coefficient Model and comparative advantage:

@@

\begin{center}
    y_{it}= \delta + \beta h_{it} + \theta_{i} + \phi\theta h_{it} + \tau_{i} + \epsilon_{it}

\end{center}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy II}

@@

\begin{itemize}
    \item Implementing a nonparametric panel identification
    \item Modeling time-varying characteristics to the Group Random Coefficients (GRC) model
\end{itemize}  
\end{frame}

>>>>

\author[et al]{Barriga-Cabanillas,  Chiarella, Correa, Michuda}

@@

\date[Feb 2021] % (optional)
{CGIAR-SPIA \\
February 2021}

@@

\textbf{We study how heterogeneity masks the true impact of adoption}

@@

Correlated Random Coefficient Model and comparative advantage (Suri 2011; Tjernstr\"{o}m et al. 2020; Michler et al. 2019; Barriga et al. 2018)

@@

\begin{center}
$$
    y_{it}= \delta + \beta h_{it} + \theta_{i} + \phi\theta h_{it} + \tau_{i} + \epsilon_{it}
$$  
\end{center}

@@

%---------------------------------------------------------
\begin{frame}
\frametitle{Empirical Strategy II and Extensions}

@@

\begin{itemize}
    \item Implementing a nonparametric panel identification in a novel GRC (Group Random Coefficients)
    \item Modeling and incorporating time-varying characteristics 
    \item Complement ESS data with precipitation (CHIRPS) and temperature (CPC) data
\end{itemize}  
\end{frame}
